\sysfull

### 2018-04-15 paper/intro.tex
References to sections updated, coala temporary online link changed, refs to alpaca and capybara removed from summary of contributions

\begin{itemize}
\item The first {\em adaptive} task-based intermittent execution model that dynamically coalesces tasks to avoid unnecessary commit overhead. 
\item The first software memory virtualization mechanism for an intermittent system that \sys uses to preserve the atomicity of coalesced tasks.
\item A fall-back dynamic task splitting mechanism that preserves forward progress despite executing tasks that are too large for a device's energy supply.
\item A fully-realized prototype of \sys that runs on real energy-harvesting devices~\cite{wisp,capybara}, to be released as open source after publication\footnote{An anonymized version of the \sys repository is already accessible via~\cite{coala_website} for inspection.}. 
\item An evaluation directly comparing \sys to a state of the art task-based intermittent programming and execution model from prior work~\cite{alpaca}, showing that on a suite of benchmarks from the literature and several new workloads, \sys often has higher performance and is more flexible to varied energy conditions. 
\end{itemize}

Section~\ref{sec:background} provides background on intermittent computing.
Section~\ref{sec:overview} provides an overview of \sys, while
Sections~\ref{sec:coalescing} and~\ref{sec:memory} describe \sys's coalescing
and virtualization mechanisms. Section~\ref{sec:discussion} discusses \sys
design issues. Sections~\ref{sec:methodology} and~\ref{sec:eval} describe
\sys's methodology and evaluation. Section~\ref{sec:related} puts \sys in the
context of related work and Section~\ref{sec:conc} concludes and discusses
future work.

>>>>

\begin{itemize}
\item The first {\em adaptive} task-based intermittent execution model that dynamically coalesces tasks to avoid unnecessary commit overhead. 
\item The first software memory virtualization mechanism for an intermittent system that \sys uses to preserve the atomicity of coalesced tasks.
\item A fall-back dynamic task splitting mechanism that preserves forward progress despite executing tasks that are too large for a device's energy supply.
\item A fully-realized prototype of \sys that runs on real energy-harvesting devices, to be released as open source after publication\footnote{The \sys repository will be accessible via~\cite{coala_website} immediately after publication.}. 
\item An evaluation directly comparing \sys to a state of the art task-based intermittent programming and execution model from prior work, showing that on a suite of benchmarks from the literature and several new workloads, \sys often has higher performance and is more flexible to varied energy conditions. 
\end{itemize}

Section~\ref{sec:background} provides background on intermittent computing.
Section~\ref{sec:systemdescription} provides an overview of \sys, while
Sections~\ref{sec:task_adaptation} describe \sys's task adaptation mechanism (coalescing and downscaling). Memory virtualization mechanisms is provided in Section~\ref{sec:memory_virtulaization}. Implementation details of \sys are give in Section~\ref{sec:implementation}. Section~\ref{sec:discussion} discusses \sys
design issues. Sections~\ref{sec:methodology} and~\ref{sec:evaluation} describe
\sys's methodology and evaluation, respectively. Section~\ref{sec:related_work} puts \sys in the
context of related work and Section~\ref{sec:conclusions} concludes and discusses
future work.
